%\chapter{Acknowledgements}%The star removes the entry from the bibliography - add manually for the reading version
{\Large\textbf{Acknowledgements}}
\chaptermark{Acknowledgements}

I am grateful to the many people who have inspired, challenged and supported me throughout my PhD trajectory. I extend my gratitude and indebtedness first and foremost to the rural households that shared a small part of their stories with us. I also wish to express my gratitude to the enumerators who guided these detailed and at times sensitive discussions.

To my promotor, Imke de Boer, thank you for asking such challenging questions, for the frank and open discussions and for hosting me. To your credit, you have cultivated a high performing and supportive work culture, for which I am glad to have been a part. To my co-promotor Simon Oosting, thank you for your support, for sharing your insights and for your dedicated input right up to submission. To my co-promotor Mark van Wijk, your leadership and collaborative spirit has provided exciting opportunities to better understand the circumstances of rural households across Africa, Asia and south-central America. I am grateful for your insights, feedback and encouragement. You have shaped and enriched this thesis and have given me the freedom to make this research my own. Thank you. 

To my unofficial supervisor, Mats Lannerstad, you were instrumental in the formation of this PhD project and have been an active contributor throughout my PhD trajectory. Your leadership in the CLEANED project provided me with immense opportunities to develop my research capacities. I would also like to thank you for the brainstorming sessions, critical feedback and well-timed bouts of laughter.  

To my other highly esteemed co-authors, it has been a pleasure to work with you all. I would like to take the opportunity to single out a few individuals in this public acknowledgement. The development and refinement of the RHOMIS tool was driven by James Hammond, with many, many hours of dutiful labour. It was great to collaborate and share in a genuine commitment to improve the standard of living in rural communities. I would like to express my gratitude to Mario Herrero, Nils Teufel, Todd Rosenstock, Jacob van Etten, Tim Pagella, Bernard Vanlauwe, Augustine Ayantunde and Ken Giller. As co-authors, you provided thought provoking comments and as scientists you have set the bar high -- thank you. Thank you to Jessica Bogard and Mary Ng'endo for the discussions on human nutrition. Thank you to George Sayula and Viviane Yameogo for your dedication to the communities in Lushoto and northern Burkina Faso. Thank you to Pietro Carpena, David Baines and the team at TreeAID for their tireless efforts to support the most vulnerable rural communities. 

From my early research career in Australia, I would like to thank Helen Scarborough and Phil Hone; thank you to Tim Ada, and the fine people in the `Agribusiness team', the Rutherglen research centre and the Ellinbank research center; thank you to John Moran; thank you to Zita Ritchie and the `grads'; thank you to Robyn Alders and the Kyeema team, and; thank you to Richard Eckard for your support.  

Thank you to my colleagues in ILRI for sharing your wealth of knowledge and for your camaraderie. To name but a few, I would like to thank Isabelle Baltenweck, Amos Omore, Ben Lukuyu, Karen Marshall, Jane Poole, An Notenbaert and Carlos Queros; Thomas Randolph and Delia Grace Randolph; Todd Crane, Katie Tavennar and Stanley Ng'ang'a; Edmund Githoro, Simon Mugatha, Eunice Kariuki, Emmanuel Kithuna, Julius Githingi, Leone Mawa, Gregory Sikumba and Jusper Ronno; Beth Njoroge, Pauline Aluoch and Assenath Kabugi; Asaah Ndambi and Patric Brandt. Thank you to Polly Ericksen for your support during my PhD.

Thank you to Pierre Gerber for providing such interesting research topics earlier in my career and for taking an interest in my PhD trajectory. Thank you to Theun Vellinga for the very early brainstorming on my PhD.

I would like to thank the WIAS staff. I thank the scientific director Johan van Leeuwen for his leadership and for taking an active role in the delivery of PhD courses. Thank you to the WIAS secretariat Janneke van Seters, Marianne Bruining and Bernie Coenders. Thank you to my study advisor Guido Bosch. Thank you to Walter Gerrits and Michiel Kleerebezem for the critical feedback on my proposal.

To the team at APS, I would like to express my sincere and heartfelt gratitude for welcoming and supporting me. To Eddie Bokkers, Kees van Reenen and Henk Udo, thank you for your leadership in the group. To Theo Viets and Fokje Steenstra, thank you for your tireless efforts in the group and for modelling what it is to be educators with impact. To Lia Verheijen, thank you for your support and good humour. I have really enjoyed the discussions (without boundaries), walks and outings with APS. I am grateful for your focus on (human) animal welfare -- you have been a kind and generous source of support. Thank you to Aart van der Linden, Abigail Muscat, Aimable Uwizeye, Akke Kok, Alejandro Parodi, Brain Akakpo, Cindy Klootwijk, Corina van Middelaar, Evelien de Olde, Hannah van Zanten, Heleen van Kernebeek, Iris Boumans, Laura Webb, Louise Kremer, Margret Wenker, Ollie van Hal, Pim Mostert, Pim Post, Raimon Ripoll Bosch, Salome `Sally' Migose, Simon Nyokabi, Titis Apdini, Windi al Zahra and Ylva Ran.

Thank you to my colleagues in the Plant Production Systems group. Jannike Wichern, I really enjoyed our in-depth discussions on food security and rural livelihoods -- it has been great to be on this journey with you. Joost van Heerwaarden, Wytze Marinus, Eva Thuijsman, Anne de Valença, I enjoyed our discussions. I am grateful to the team at CDI for providing opportunities to carry out my pedogeological training. In particular, thank you to Ted Schrader and Diane Bosch. Thank you to Bas Engel for the enlightening discussions on statistics. Thank you to Emmanual Koyano for translating the summary of this thesis into Kiswahili. 

I would also like to express my sincere gratitude to the members of the committee for taking the time to evaluate my thesis and to participate in the public defense.

Thank you to my dear parents for cultivating my curiosity, diligence, and compassion. Thank you to my brothers, sisters, nephews and nieces for the inspiration that you have given me. Thank you to Roland Fraval, Shari Cohen and the good people of Brunswick who made me feel at home in my hometown during the analysis phase of my PhD. Rafiki zangu kutoka Afrika Mashariki -- asanteni sana. Ulinikaribishwa na hunifundisha sana sana. Pamoja na neema ya Mungu, natumaini tutaboresha maisha ya watu wanaopunguzwa.     

%\lipsum[1-9]

